Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
add todo spat scale

### Spatial scale

To assess the influence of spatial scale, we aggregated the land cover raster at
varying scales relevant to caribou ecology. We aggregated the original 30 m land
cover raster using the R package `grainchanger` [@Graham_2019] across a series
of scales (100 - 1000 m by steps of 100 m) The land cover raster was aggregated
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
decision making for caribou during foraging, while re-sampling at 500 m , 750 m
and 1000 m represents the scale at which caribou tend to select and avoid
habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.

>>>>

### Spatial scale
<!-- TODO: Increased spatial scale of land cover corresponds to xyz -->
To assess the influence of spatial scale, we aggregated the land cover raster using the R package `grainchanger` [@Graham_2019] across a series
of scales (100 - 1000 m by steps of 100 m). The land cover raster was aggregated
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
decision making for caribou during foraging, while re-sampling at 500 m , 750 m
and 1000 m represents the scale at which caribou tend to select and avoid
habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.
